Variability in upwelling patterns across the Benguela region

### 2019-10-09 Write_up/Paper1_writeup.Rmd
draft_writeup

The linear regression analysis showed that the cumulative intensity among all variables within each dataset showed the most variation. The cumulative intensity acts as absolute magnitude rather than relative seasonal climatology. When looking at the results for the data obtained from the OISST dataset it is evident that R^2 values are highest at greater distances from the coastline for each of the sites except for Port Nolloth. For examples, Lamberts Bay had an R^2 value of 5.47  at a distance of 10000km but only an R^2 value of -8.76 at 50000km. Similar trends were apparent for Saldanha Bay (R^2 -3.28 at 10000 km and -12.42 at 50000 km) and Sea Point (R^2  = -8.77 at 10000 km)

The CMC remotely sensed sea surface temperature dataset had higher R^2 values compared to the OISST dataset. Most of the sites within CMC dataset had greater R^2 values at distances furthest from the coastline. Here, Lamberts Bay had R^2 value of -26.30 for 10000km and -31.77 for 50000km respectively. Similarly, Port Nolloth had R^2 values of -15.34 at 10000km and -20.45 at 50000km. Saldanha Bay however presented its lowest value of -24.84 at 10000km and highest R^2 value of -46.39 at 40000km and also the highest value among all of the sites. Additionally, Sea Point displayed similar patterns with the lowest value occurring at a distance of 10000km from the coastline and its highest R^2 value of -38.35 occurring at a distance of 40000km from the coastline.

Lastly, the SACTN in situ collected SST data collected directly at the coastline had variable R^2 values. Lamberts Bay had an R^2 value of -1.46. Port Nolloth, representing the second highest value of -3.65. Saldanha Bay representing an R^2 value of -2.56 and the highest R^2 value of -10.96 occurring at Sea Point.

>>>>

The regression slope shows the slope of the trend for each of the datasets used within this study. When looking at the OISST dataset, it is eveident that there is no contstant trend among sites. It is evident however that the strongest trends exist at 10km from the coastline, with the weakest trends occuring at a distance of 30 – 40km from the coastline. In the CMC dataset events occuring at a distance of 10km from the coastline shows the strongest trend compared to trends observed at a distance of 50km from the coasltine. In this dataset we see that at a distance of 10km, Lamberts Bay shows that every decade upwelling lasts for approximatly 3days longer. Similarly, Port Nolloth shows that upwelling lasts for approximately 2 days longer. Both Saldanha Bay and Sea Point shows a trend of upwelling lasting for approximately 3 days more. When looking at the in situ collected temperatur data the trend represents an increase of 1 additional day per decade for each of the sites expect Saldanha Bay. Here Saldanha Bay represent a trend value of 0.37 which largely varies with the trend values obtained from the OISST and CMC dataset.
